%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{article} % Document font size and paper size

\usepackage{fontspec} % Allows the use of OpenType fonts

%\usepackage{geometry} % Allows the configuration of document margins
%\geometry{textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in} % Document margin settings
\usepackage[margin=1in,top=1in, bottom=1in]{geometry}
\setlength\parindent{0in} % Remove paragraph indentation

\usepackage[usenames,dvipsnames]{xcolor} % Custom colors

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\reversemarginpar

\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Alejandro Ochoa CV},pdfauthor={Alejandro Ochoa}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} % Link colors

% MATH stuff (limited)
\usepackage{xspace}
\usepackage{amsmath,amsfonts,amssymb}
\newcommand{\Fst}{\ensuremath{F_{\text{ST}}}\xspace}

%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Linux Libertine Font (default)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\sectionfont{\mdseries\upshape\Large} % Set font options for sections
\subsectionfont{\mdseries\scshape\normalsize} % Set font options for subsections
\subsubsectionfont{\mdseries\upshape\large} % Set font options for subsubsections
\chardef\&="E050 % Custom ampersand character

%----------------------------------------------------------------------------------------

\begin{document}

\begin{center}
  {\LARGE Alejandro Ochoa}\\[0.5cm] % Your name
  Duke Center for Statistical Genetics and Genomics\\
  Department of Biostatistics and Bioinformatics\\
  Fitzpatrick Center for Interdisciplinary Engineering, Medicine and Applied Sciences (CIEMAS)\\
  101 Science Dr, Room 2177C\\
  Durham, NC 27705\\
  \href{mailto:alejandro.ochoa@duke.edu}{alejandro.ochoa@duke.edu}\\ % Your email address
  \url{https://ochoalab.github.io/} \\ % http://viiia.org/research % Your academic/personal website
\end{center}

%\vfill % Whitespace between contact information and specific CV information

%\section*{Research Interests}
%Statistics, Bioinformatics, Computational Biology\\ % Your primary areas of research interest
%Population Genetics\\
%Protein Sequence Evolution and Function\\
%Human, Malaria Parasites

\section*{Education}

\years{2013}
PhD in Molecular Biology, Princeton University
\\
Dissertation:
\emph{Protein domain prediction using context statistics, the false discovery rate, and comparative genomics, with application to Plasmodium falciparum}
\\
Advisers:
Mona Singh (Computer Science) and Manuel Llinás (Molecular Biology)
\\
\years{2006}
\textsc{BS} in Biology and Mathematics, Massachusetts Institute of Technology

\section*{Awards \& Honors}

\years{2022}
Lathisms: showcase of contributions of Latinx and Hispanic mathematicians during Hispanic Heritage Month.
\url{https://www.lathisms.org/calendars/calendar-2022}
\\
\years{2020}
Whitehead Scholar, Whitehead Charitable Foundation.
For Duke junior faculty with exceptional potential for research and research training in the biomedical sciences.
\\
\years{2008}
NSF Graduate Research Fellowship.
Computational Biology.
\\
\years{2008}
Ford Foundation Diversity Fellowship Predoc. Comp.
(Declined, listed as Honorable Mention.)
\\
\years{2006}
MIT Department of Biology Merck Prize.
Awarded to a graduating senior for outstanding research and academic performance in biophysics or bioinformatics.
\\
\years{2001}
Mexican Math Olympiad Gold Medal.
Awarded to top 15 competitors nationally.

\section*{Employment}

\years{2018-now}\emph{Assistant Professor},
Duke Center for Statistical Genetics and Genomics, 
Department of Biostatistics and Bioinformatics,
Duke University\\
\years{2013-2018}\emph{Postdoctoral Research Associate} at John D Storey's group,
Lewis-Sigler Institute for Integrative Genomics, and
Center for Statistics and Machine Learning,
Princeton University

\section*{Publications}

\input{pubs.tex} % generated automatically!

\section*{Distributed software}

\input{software.tex} % generated automatically!

\section*{Invited Talks}

\input{talks.tex} % generated automatically!

\section*{Conference posters}

\input{posters.tex} % generated automatically!

\section*{Teaching}

\subsection*{Duke University}
\years{2022-2024}Human Genetics. (Co-Lecturer Spring 2022-2024)\\
\years{2021-2024}UPGEN 778A-F Mini course: Genetic population structure and relatedness (Fall 2021-2024)\\
\years{2019-2024}SIBS lecture on genetic association studies (Summer 2019, 2021-2024)\\
\years{2019}BIOS 900 Current Problems in Biostatistics. Special lecture on kinship and \Fst\\
\years{2019}BIOS 710 Statistical Genetics and Genetic Epidemiology. Special lecture on kinship and \Fst

\subsection*{Princeton University}
\years{2017}Intro to Genomics and Comp Bio.  Quant Comp Bio, Comp Sci. (Co-Lecturer Fall 2017)\\
\years{2016-2017}Discussion Leader.  Summer Undergraduate Research Program (Summer 2016, 2017)\\
\years{2014-2017}Statistical Treatment of Data. Mol Bio, Quant Comp Bio. (Workshop Fall 2014-2017)\\
\years{2011}Intro to Genomics and Comp Mol Bio.  Mol Bio, Comp Sci. (TA Fall 2011)\\
\years{2008}Core Laboratory. Mol Bio. (TA Spring 2008)

\subsection*{Massachusetts Institute of Technology}
\years{2005}Calculus. OME Project Interphase (TA Summer 2005)\\
\years{2003-2004}Multivar Calculus and Diff Eqs. OME Seminar XL (Tutor Fall 2003, Spring 2004)\\
\years{2003-2004}Calculus. MITE2S Program (TA Summer 2003, 2004)

\section*{Mentoring}

\input{students.tex} % generated automatically!

\section*{Research experience}

\years{2018-now} Principal investigator, Duke.  I lead a team of trainees (graduate students, postdocs, master students and undergraduates) pursuing original research in statistical genetics and computational biology.  Our lab focuses on models and applications for structured populations, including multiethnic and admixed cohorts and modeling cryptic relatedness.\\
\years{2013-2018} Postdoctoral Research, Storey Lab, Princeton. Developed new definitions and tools to study arbitrary population structures. Also applied GWAS and mixed effects modeling to longitudinal psychiatric drug clinical trials.\\
\years{2007-2013} Graduate Research Thesis, Singh Lab and Llinás Lab, Princeton.  Developed probabilistic models and statistical methods that improve protein domain prediction.  Studied the \emph{Plasmodium falciparum} proteome, focusing on the AP2 transcription factors.  Used experimental techniques (cloning, protein purification and protein-binding microarrays) to test predicted AP2 domains for DNA binding.\\
\years{2007} Graduate Rotation, Tavazoie Lab, Princeton. Cloned an RNA aptamer for a phage display assay.\\
\years{2006-2007} Graduate Rotation, Singh Lab, Princeton. Analyzed protein interactions predicted from the presence of interacting domain pairs.\\
\years{2006} Graduate Rotation, Troyanskaya Lab, Princeton.  Built and analyzed a potential "gold standard" of Gene Ontology terms integrated from predictions of multiple sources, in \emph{Saccharomyces cerevisiae} and \emph{Homo sapiens}.\\
\years{2005-2006} Undergraduate Research Assistant, Keating Lab, MIT.  Analyzed full-atom computational protein designs using modified van der Waals potentials.

%\section*{Service to the profession}
%\years{2015} Reviewed a manuscript for the RECOMB 2016 conference.\\
%\years{2014} Reviewed a manuscript for PLoS Computational Biology.\\
%\years{2011} Reviewed a manuscript for BMC Bioinformatics.

\section*{Organizations}

\years{2023-now} American Mathematical Society (AMS).  Member.\\
\years{2020-now} American Society of Human Genetics (ASHG). Member.\\
\years{2006-2010} Latino Graduate Student Association, Princeton University. Board member: Technology Specialist 2007-2010 (handled website, email list, photos, calendar).\\
\years{2002-2006} Association of Puerto Rican students, MIT. Member.

\section*{Outreach, admissions, committees, and other service}

\years{2020-now}Duke Center for Combinatorial Gene Regulation: Outreach and Engagement.
Funded by a NIH Centers for Excellence in Genomics Science (CEGS) grant.
Includes the Duke Genomic Scholars Program: providing accessible genomic training for a diverse workforce.  Duke University.\\
\years{2019-now}B\&B Diversity and Inclusion Committee.  Duke University.\\
\years{2019-2024}CBB PhD Admissions Committee.  Duke University.\\
\years{2024}Promise and pitfalls of polygenic risk scores, faculty and postdoc panel, Triangle Center for Evolutionary Medicine’s (TriCEM) annual Evolutionary Medicine Summer Institute (EMSI).\\
\years{2024}B\&B retreat, moderated session on Research Working Group.  Duke University.\\
\years{2024}Using Race, Ethnicity \& Ancestry as Population Descriptors in Genetics and Genomics Research (NASEM report symposium), faculty panel.  Duke University.\\
\years{2023}CBB retreat, faculty panel.  Duke University.\\
\years{2023}Genomic Scholars Program, faculty panel.  Duke University.\\
\years{2023}Session moderator, 021: Human genome evolving I. ASHG annual meeting.\\
\years{2023}Abstract reviewer, topic Evolutionary and Population Genetics. ASHG annual meeting.\\
\years{2022}Session moderator, S41: Populations evolving: Modeling genetic variation to understand evolutionary processes.  ASHG annual meeting.\\
\years{2021-2022}Faculty Committee Member, Duke Next Generation Leaders.  Duke University.\\
\years{2021}B\&B Faculty Search Committee.  Duke University.\\
\years{2021}B\&B Master of Biostatistics Virtual Visit Day.  Duke University.\\
\years{2019}B\&B informational interviewing practicum.  Duke University.\\
\years{2017}Panelist at HISPA Latinos in College Conference. Princeton University.\\
\years{2010}Ivy-plus recruiting fair at University of Puerto Rico (4 campuses) for Princeton.\\
\years{2008-2011}Science and Engineering Expo. HHMI and Princeton University.\\
\years{2008}Graduate school recruiting, student group panel, I represented the Latino Graduate Student Association (LGSA).  Princeton University.\\
\years{2007}Helped local high school students with college personal statements. PUPP, Princeton University.

\section*{Languages}

English. Native proficiency.\\
Spanish. Native proficiency.\\
French. Fluent reading and writing, conversational speaking.

\vfill{} % Whitespace before final footer

%----------------------------------------------------------------------------------------
%	FINAL FOOTER
%----------------------------------------------------------------------------------------

\begin{center}
  {\scriptsize Last updated: \today} % Any final footer text such as a URL to the latest version of your CV, last updated date, compiled in XeTeX, etc
  % \- •\- \href{http://www.LaTeXTemplates.com}{http://www.LaTeXTemplates.com}
\end{center}

%----------------------------------------------------------------------------------------

\end{document}
